---
title: "Informative title"
author: "Name"
date: "Date"
abstract: "Four sentences"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("tidyverse")
install.packages("remotes")
remotes::install_github("hodgettsp/cesR")
library(tidyverse)
library(visdat)
library(cesR)
library(skimr)
```

# Introduction

Three paragraph statement.

First paragraph: General. Motivational. Majors specific finding. 

Second paragraph: More about what you did and found.

Third paragraph: Outline of the paper. Future work. Weaknesses.


```{r download, warning=FALSE, message=FALSE}
cesR::get_decon()
```

# Data

The CES dataset is....

```{r}
head(decon)
```
Some initial explorations that would be used to guide this section.

```{r}
visdat::vis_dat(decon)

skimr::skim(decon)

class(decon$ces_code)

decon <- 
  decon %>% 
  filter(income < 1000000)

decon <- 
  decon %>% 
  select(religion, income)
```


The variables we focus on are....

Summary statistics for these variables...

You must include graphs.


```{r}
decon %>% 
  ggplot(aes(x = religion)) +
  geom_bar()
```


```{r}
decon %>% 
  ggplot(aes(x = income)) +
  geom_histogram()
```



```{r}
decon %>% 
  ggplot(aes(x = income)) +
  geom_histogram() +
  labs(x = "Income",
       y = "Number",
       title = "Distribution of income in 2019 CES",
       caption = "Source: Stephenson, Harell, Rubenson, Loewen, 2020.") +
  theme_bw()
```

In this graph we find that the distribution of income is heavily skewed....




# Discussion

My discussion... main findings of your graph.


Features of your survey.... Non-response... etc. And how these could affect the results....




## Weaknesses and next steps

My weaknesses...






# References

- Stephenson, Laura B; Harell, Allison; Rubenson, Daniel; Loewen, Peter John, 2020, '2019 Canadian Election Study - Online Survey', https://doi.org/10.7910/DVN/DUS88V, Harvard Dataverse, V1
- Paul A. Hodgetts and Rohan Alexander (2020). cesR: Access the CES Datasets a Little Easier.. R package version 0.1.0.
-  Hadley Wickham, Jim Hester and Winston Chang (2020). devtools: Tools to Make Developing R Packages Easier. https://devtools.r-lib.org/,https://github.com/r-lib/devtools.
- R Core Team (2020). R: A language and environment for statistical computing. R, Foundation for Statistical Computing, Vienna, Austria. URL, https://www.R-project.org/.
- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron Atkins and Hadley Wickham and Joe Cheng and Winston Chang and Richard Iannone (2020). rmarkdown: Dynamic Documents for R. R package version 2.3. URL https://rmarkdown.rstudio.com.




